---
title: "Part 1: Fechner's & Stevens' Laws"
output: pdf_document

header-includes:
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r Library}
library(tidyverse)
```

# Part 1

## Part 1.2 Draw some illustrative graphs

| **For stimulus intensities ranging between 1 and 100, plot a graph illustrating the different predictions of Fechner’s Law and Stevens’ Law, using parameter (j, k and a) values that enable the comparison to be clear**

$\text{Fechner's Law: } S = k \times \log{j}$

-   `S` = Subjective magnitude (i.e., stimulus perceived strength)

-   `k` = Parameter (i.e., constant that depends on what sense is being measured)

-   `j` = Stimulus intensity (i.e., objective stimulus strength)

$\text{Stevens' Law: }S = k \times j^{a}$

-   `S` = Subjective magnitude (i.e., stimulus perceived strength)

-   `k` and `a` = Parameters (i.e., constants)

-   `j` = Stimulus intensity (i.e., objective stimulus strength)

\newpage

```{r Fechner_Stevens}
### FUNCTION CALCULATING SUBJECTIVE MAGNITUDE ACCORDING TO FECHNER'S AND STEVENS' LAWS ###

fechner_stevens <- function(j_intensity, k, a) {
  
  # ESTABLISH EMPTY VECTORS
  fechner <- c()
  stevens <- c()
  
  
  for (j in j_intensity) {
    # CALCULATE SUBJECTIVE MAGNITUDE FOR EACH LAW
    fechner_values <- k * log(j)
    stevens_values <- k * j^(a)
    
    # APPEND RESULTS TO RESPECTIVE VECTOR
    fechner <- c(fechner, fechner_values)
    stevens <- c(stevens, stevens_values)
  }
  
  
  # CREATE TIBBLE OF SUBJECTIVE MAGNITUDES OF EACH LAW
  subjective_magnitudes <- tibble("stimulus_intensity" = j_intensity,
                                  "Fechner's law" = fechner,
                                  "Stevens' law" = stevens)
  
  subjective_mag <- subjective_magnitudes %>% 
    ## Pivot longer to make a tidy tibble
    pivot_longer(c("Fechner's law", "Stevens' law"), 
                 names_to = "Law", 
                 values_to = "subjective_magnitudes") %>% 
    ## Establish each `a` parameter as a unique factor
    mutate(Law = factor(Law, levels = unique(Law)))
  
  
  # PLOT GRAPH 
  plot <- ggplot(data = subjective_mag, 
         aes(x = stimulus_intensity, y = subjective_magnitudes, col = Law)) +
    geom_point() +
    geom_line() +
    
    ## Rename axes
    labs(title = "Fechner's vs Stevens' Laws",
         subtitle = paste0("When k = ", k, " and a = ", a),
         x = "Stimulus Intensity (j)",
         y = "Subjective Magnitudes (S)") +
    
    ## Set theme
    theme_bw()
  
  return(list(table = subjective_mag, graph = plot))
  
}
```

\newpage

```{r Comparison_k}
### VARYING VALUES OF PARAMETER k ###

k_values <- c(seq(0, 10, 5))

for (k in k_values) {

  fs <- fechner_stevens(j_intensity = c(1:100), k = k, a = 0.5)
  print(fs)
  print("--------------------------------------------------------------")
  print("--------------------------------------------------------------")
  print("--------------------------------------------------------------")

}
```

\newpage

```{r Stevens_a_Function}
### FUNCTION APPLYING STEVENS' LAW TO DIFFERENT a PARAMETERS ###

stevens_a <- function(j_intensity, k, a_parameter, table = FALSE, graph = FALSE) {
  
  # ESTABLISH VARIABLES FOR LENGTHS OF a_parameter AND j_intensity
  a_n <- length(a_parameter)
  j_n <- length(j_intensity)
  
  
  # ESTABLISH EMPTY VECTOR
  stevens <- c()
  
  
  # LOOPING THROUGH EVERY a PARAMETER 
  for (a in a_parameter) {
      
    # LOOPING THROUGH EVERY STIMULUS INTENSITY VALUE (j)
    for (j in j_intensity) {
      
      # CALCULATE SUBJECTIVE MAGNITUDE FOR STEVENS' LAW
      stevens_values <- k * j^(a)
      
      # APPEND SUBJECTIVE MAGNITUDES TO EMPTY VECTOR
      stevens <- c(stevens, stevens_values)
  
    }
  }
  
  # CREATE TIBBLE OF SUBJECTIVE MAGNITUDES FOR EACH a PARAMETER
  a_tibble <- tibble("a" = rep(a_parameter, each = j_n),
                     "k" = rep(k),
                     "stimulus_intensity" = rep(j_intensity, times = a_n),
                     "stevens_pred" = stevens)
  
  ## Establish each `a` parameter as a unique factor
  a_tibble <- a_tibble %>% 
    mutate(a = factor(a, levels = unique(a)))
  
  
  # PRINT TABLE & GRAPH IF BOTH ARE CALLED
  if (table && graph == TRUE) {
    plot <- ggplot(data = a_tibble,
                   aes(x = stimulus_intensity, y = stevens_pred, colour = a)) +
    geom_line() +
    
    ## Naming titles and axes
    labs(title = "Stevens' Law Applied to Different a Parameters",
         subtitle = paste0("When j = ", min(j_intensity), ":", max(j_intensity), " and k = ", k),
         x = "Stimulus intensity (j)" ,
         y = "Subjective Magnitudes (S)" ,
         colour = "a") +
    
    ## Set theme
    theme_bw()
    
    return(list(table = a_tibble, graph = plot))
  }
  
  
  # PRINT TABLE IF CALLED
  else if (table) {
    return(a_tibble)
  }
  
  
  # PRINT GRAPH IF CALLED
  else if (graph) {
    plot <- ggplot(data = a_tibble,
         aes(x = stimulus_intensity, y = stevens_pred, colour = a)) +
    geom_line() +
    
    ## Naming titles and axes
    labs(title = "Stevens' Law Applied to Different a Parameters",
         subtitle = paste0("When j = ", min(j_intensity), ":", max(j_intensity), " and k = ", k),
         x = "Stimulus intensity (j)" ,
         y = "Subjective Magnitudes (S)" ,
         colour = "a") +
    
    ## Set theme
    theme_bw()
    
    return(plot)
  }
  
}
```

\newpage

```{r Comparison_a}
# stevens_a(1:20, 1, 0.67, table = TRUE, graph = TRUE)

### VARYING VALUES OF PARAMETER a ###

a_values <- c(seq(0, 1, 0.25), 2)

for (a in a_values) {

  fs <- stevens_a(j_intensity = c(1:100), k = 5, a = a, graph = TRUE)
  print(fs)
  print("--------------------------------------------------------------")
  print("--------------------------------------------------------------")
  print("--------------------------------------------------------------")

}
```

\newpage

```{r a_exponents}
### APPLYING STEVENS' LAW TO DIFFERENT STIMULI TYPES ###


# ESTABLISH VARIABLES
## Stimuli intensity
j_int_data <- c(1:50)
j_int_n <- length(j_int_data)

## Parameter k
brightness_k <- 10
loudness_k <- 10
heaviness_k <- 0.1
electric_k <- 0.0001


# CALCULATES STEVENS' LAW FOR EACH STIMULI
Brightness <- stevens_a(j_int_data, brightness_k, 0.5, table = TRUE)
Loudness <- stevens_a(j_int_data, loudness_k, 0.67, table = TRUE)
Heaviness <- stevens_a(j_int_data, heaviness_k, 1.45 , table = TRUE)
Electric <- stevens_a(j_int_data, electric_k, 3.5 , table = TRUE)


# CREATE TABLE INCLUDING STIMULI NAMES
## Important for legend names
stimuli_name <- c(paste0("Brightness (a = 0.5, k = ", brightness_k, ")"), 
                  paste0("Loudness (a = 0.67, k = ", loudness_k, ")"), 
                  paste0("Heaviness (a = 1.45, k = ", heaviness_k, ")"), 
                  paste0("Electric Shock (a = 3.5, k = ", electric_k, ")"))

new_stimuli <- rbind(Brightness, Loudness, Heaviness, Electric)

new_stimuli <- new_stimuli %>% 
  as_tibble() %>% 
  mutate(stimuli = rep(stimuli_name, each = j_int_n)) %>% 
  relocate(stimuli, .before = a) %>% 
  mutate(stimuli = factor(stimuli, levels = unique(stimuli)))

new_stimuli


# CREATE PLOT
ggplot(data = new_stimuli,
       aes(x = stimulus_intensity, y = stevens_pred, colour = stimuli)) +
    geom_line() +

    ## Naming titles and axes
    labs(title = "Stevens' Law Applied to Different Stimuli",
         subtitle = paste0("When j = ",
                           min(new_stimuli$stimulus_intensity), ":", 
                           max(new_stimuli$stimulus_intensity)),
         x = "Stimulus intensity (j)" ,
         y = "Subjective Magnitudes (S)" ,
         colour = "Stimuli") +

    ## Set theme
    theme_bw()
```

\newpage

## Part 1.3 Comparing model and data

Imagine you present six stimuli (e.g., tones varying in loudness) to participants, multiple times, and ask them to rate on a 1-7 scale how loud they are.

1.  **Calculate the RMSD (root mean square deviation) between model (Stevens’ Law) and judgements for various parameter values**

    -   Explore the *model’s predictions* for the judgements of subjective intensities of these sensory magnitudes: `stimuli = [2, 4, 6, 8, 10, 12]`

    ```{r RMSD_Function}
    ### FUNCTION CALCULATING RMSD USING TABLE OUTPUT FROM stevens_a FUNCTION ###

    rmsd_calc <- function(stevens_func_table, actual_judgements) {
      
      # MODEL PREDICTIONS
      model_pred <- stevens_func_table

      a_n <- model_pred$a %>%
        unique() %>% 
        length() 
      
      
      # ACTUAL JUDGEMENT
      model_actual <- model_pred %>% 
        mutate(actual_judgements = rep(actual_judgements, times = a_n)) %>% 
        relocate(k, .before = a)

      
      # CALCULATE SD
      sd_table <- model_actual %>% 
        mutate(sd = (stevens_pred - actual_judgements) ^ 2,
               a = factor(a, levels = unique(a)),
               k = factor(k, levels = unique(k))
               ) 
      
      ## Identify k (for title)
      k <- unique(sd_table$k)
      
      
      # CALCULATE RMSD
      rmsd_table <- sd_table %>%
        group_by(a) %>%
        mutate(rmsd = sqrt(mean(sd)))
      
      ## Print table (for checking purposes)
      print(rmsd_table)
      
      ## Select columns (for graph)
      rmsd_graph <- rmsd_table %>% 
        select(1:2, 7) %>%
        group_by(a) %>%
        summarise(RMSD = round(mean(rmsd), 2))
      
      y_max <- max(rmsd_graph$RMSD)
      
      # PLOT GRAPH
      ggplot(data = rmsd_graph,
             aes(x = a, y = RMSD)) +
        geom_bar(stat = "identity") +
        geom_text(aes(label = RMSD), vjust = -0.5, size = 3) +
        labs(title = paste0("RMSD as `a` changes when k = ", k)) +
        theme_bw()
    }
    ```

    \newpage

    2.  **Find the approximate parameter values that minimise RMSD**
        -   An experiment was conducted to find the actual subjective intensities in human participants: `judgements = [1.1, 1.5, 2.1, 2.5, 2.9, 3.2]`
        -   **What values of a and k will minimise RMSD?**

    ```{r RMSD}
    ### CALCULATING RMSD ###

    # DEFINING ARGUMENTS
    j_data <- seq(2, 12, 2)
    # a <- c(0.5, 0.67, 1.45, 3.5)
    a <- c(seq(0, 5, 0.5))
    actual_judgements <- c(1.1, 1.5, 2.1, 2.5, 2.9, 3.2)


    # VARIABLES OF OUTPUT FROM stevens_a FUNCTION
    pred_k1 <- stevens_a(j_data, 1, a, table = TRUE, graph = TRUE)
    pred_k10 <- stevens_a(j_data, 10, a, table = TRUE, graph = TRUE)


    # CALLING rmsd_calc 
    rmsd_calc(pred_k1$table, actual_judgements)
    rmsd_calc(pred_k10$table, actual_judgements)
    ```
