---
title: "Part 2: Range Frequency Theory (RFT)"
output: pdf_document

header-includes:
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Library}
library(tidyverse)
library(scales)
```

# Task 2 Data to Model

Each of the four lists of 11 numbers over gives a set of hypothetical prices for a product

For each of the four distributions separately:

1.  Determine the predicted judged “expensiveness” of each price according to RFT (with parameter `w` set to 0.5)
    -   Predicted judgements should be on a scale between 1 and 7
2.  Plot graphs to illustrate the predictions
3.  Explore and briefly describe the effects of varying `w`

## Modelling Strategy

```{r Models}
# ASSIGNING PRICES TO A MODEL VECTOR
unimodel <- c(28, 42, 46, 49, 52, 55, 58, 61, 64, 68, 82)
bimodel <- c(28, 31, 34, 38, 42, 55, 68, 72, 76, 79, 82)
positive_skew <- c(28, 29, 31, 33, 36, 39, 43, 48, 55, 65, 82)
negative_skew <- c(28, 45, 55, 62, 67, 71, 74, 77, 79, 81, 82)


# LIST OF ALL MODELS AND THEIR RESPECTIVE PRICES
models <- list(unimodel = unimodel,
               bimodel = bimodel,
               positive_skew = positive_skew,
               negative_skew = negative_skew)


# VECTOR OF ALL THE PRICES
full_model <- c(unimodel, bimodel, positive_skew, negative_skew)
```

1.  **Calculate “range” values for each price (make vector)**

    Rank = $\frac{s - min(model)}{max(model) - min(model)}$

2.  **Calculate “frequency” values for each price (make vector)**

    Frequency = $\frac{rank - 1} {n - 1}$

3.  **Calculate RFT prediction for each price (make vector)**

    Magnitude = $(w \times rank) + ((1 - w) \times frequency)$

4.  **The RFT values will vary between 0 and 1. These need to be transformed into predicted ratings between 1 and 7**

5.  **Draw the graphs**

6.  **Examine effect of varying the `w` parameter**

```{r Function}
### CALCULATE RFT PREDICTIONS ###

RFT_Predicted_Graph <- function(w, models_list, full_model) {

  # RFT - SUBJECTIVE MAGNITUDE (OR SUBJECTIVE JUDGEMENT)
  ## Vectors to store answers for each equation
  rank <- c()
  frequency <- c()
  magnitude <- c()
  
  for (name in names(models)) {
    model <- models[[name]]           ## Establish model of focus by name
  
    for (i in seq_along(model)) {
      s <- model[i]                   ## Element indexed i
      n <- length(model)              ## Length of model 
  
      model_max <- max(model)         ## Max value of model 
      model_min <- min(model)         ## Min value of model 
  
      ## Calculate rank
      rank_value <- (s - model_min) / (model_max - model_min)
      rank <- c(rank, rank_value)
      
      ## Calculate frequency
      frequency_value <- (rank_value - 1) / (n - 1)             
      frequency <- c(frequency, frequency_value)
      
      ## Calculate magnitude
      magnitude_value <- (w * rank_value) + ((1 - w) * frequency_value)   
      magnitude <- c(magnitude, magnitude_value)
  
    }
  }
  
  m_n <- length(model)          ## Length of model
  m_names <- names(models)      ## Names of each model
  
  
  # CREATE A TIBBLE WITH VARIABLES
  model_rfm <- tibble(index = rep(1:11, times = 4),
                      prices = full_model,
                      model = rep(m_names, each = m_n),
                      rank = rank,
                      frequency = frequency,
                      magnitude = magnitude)

  ## Ensure tibble only had key variables
  model_magnitude <- model_rfm %>% 
    select(1:3, 6)
  
  
  # RESCALING SUBJECTIVE MAGNITUDES TO PREDICTED VALUES
  predicted_ratings <- model_magnitude %>%
    mutate(predicted_ratings = rescale(magnitude, to = c(1, 7))) %>% 
    mutate(w = rep(w))

  
  # CALCULATING MEANS PER MODEL
  pr_mean <- predicted_ratings %>% 
    group_by(model) %>%
    summarize(mean_pr = mean(predicted_ratings)) %>% 
    mutate(w = rep(w))
  
  ## Upper bound for y-axis
  max_pr_mean <- round(max(pr_mean$mean_pr), 0) + 1
  
  ## Upper & Lower bounds for subjective magnitudes
  ### print(max(predicted_ratings$magnitude))
  ### print(min(predicted_ratings$magnitude))
  
  
  # GRAPHS
  ## Predicted ratings 
  pr_plot <- ggplot(predicted_ratings,
                    aes(x = index, y = predicted_ratings, colour = model)) +
    geom_point() +
    geom_line() +
    
    scale_x_continuous(name = "Element index",
                     breaks = seq(0, 11, 1)) +
    scale_y_continuous(name = "Predicted Judgements",
                     breaks = seq(0, 7, 0.5)) +
    labs(title = paste("Models of Predicted Judgements when w =", w),
         colour = "Models") +
    
    theme_bw() 
  
  ## Subjective Magnitude 
  sm_plot <- ggplot(predicted_ratings,
                    aes(x = index, y = magnitude, colour = model)) +
    geom_point() +
    geom_line() +
    
    scale_x_continuous(name = "Element index",
                     breaks = seq(0, 11, 1)) +
    scale_y_continuous(name = "Subjective Magnitude") +
    
    labs(title = paste("Models of Subjective Magnitude when w =", w),
         colour = "Models") +
    
    theme_bw() 
  
  ## Means of predicted ratings per model
  mean_plot <- ggplot(pr_mean, aes(x = model, y = mean_pr)) +
    geom_bar(stat = "identity", fill = "grey") +
    
    geom_text(aes(label = round(mean_pr, 2)),
              vjust = -0.3,
              colour = "black") +
    
    labs(title = paste("Mean Predicted Judgements per Model when w =", w),
         x = "Model",
         y = "Mean Predicted Judgements") + 
    
    ylim(c(0, max_pr_mean)) +
    
    theme_bw()
  
  
  return(list(predicted_ratings = predicted_ratings,
              sm_plot = sm_plot, 
              pr_plot = pr_plot, 
              mean_plot = mean_plot))
  
}
```

```{r RFT_Predicted_Graph}
### VARYING VALUES OF w IN RFT ###

w_values <- c(seq(0, 1, 0.25))

for (w in w_values) {
  
  RFT_pred <- RFT_Predicted_Graph(w, models, full_model)
  print(RFT_pred)
  print("--------------------------------------------------------------")
  print("--------------------------------------------------------------")
  print("--------------------------------------------------------------")
}
```
