---
title: "Part 3 Decision by Sampling (DbS)"
output: pdf_document

header-includes:
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Library}
library(tidyverse)
```

# Task 3 Explore the use of DbS to predict subjective judgement by sampling

1.  **Generate a large sample of positively-skewed random numbers from a beta distribution**

    -   **Example: `LTM <- 20 * rbeta(1000, 1.2, 4)`**

        -   This gives a sample of 1000 random values between 0 and 20 that follow a Beta distribution where $\alpha = 1.2 \text{ and } \beta = 4$

        -   The `rbeta()` function in R generates random numbers from the *Beta distribution*, which is defined by two shape parameters: `shape1` ( $\alpha$ ) and `shape2` ( $\beta$ ).

            -   When `shape1` ( $\alpha$ ) \> `shape2` ( $\beta$ ), the Beta distribution is *negatively* *skewed*

            -   When `shape1` \< `shape2`, the Beta distribution is *positively* *skewed*

            -   When `shape1` = `shape2`, the Beta distribution is *symmetrical*

2.  **Draw a histogram of these numbers using `hist`**

    ```{r Histogram}

    # CREATE A POSITIVELY SKEWED SAMPLE BASED ON A BETA DISTRIBUTION
    set.seed(1)
    pskew_sample <- 20 * rbeta(1000, 1.2, 4)

    # CONVERT THE SAMPLE VECTOR INTO A TIBBLE
    pskew_data <- tibble(values = pskew_sample)

    # FIND THE MAX AND MIN VALUES IN THE SAMPLE 
    pskew_max <- round(max(pskew_data$values), 0)
    pskew_min <- min(pskew_data$values)

    # CREATE HISTOGRAM
    hist(pskew_data$values,
         breaks = seq(0, pskew_max, 1),
         col = "white", border = "black",
         main = "Histogram of Positive Skewed Sample ",
         xlab = "Values",
         xlim = c(0, pskew_max)
         )

    ## Subtitle explaining the distribution
    mtext("Beta distribution (alpha = 1.2, beta = 4)", side = 3, line = 0.5, cex = 0.8)

    ```

3.  **Calculate the subjective judgement of magnitudes 1 through 20 based on a DbS strategy and sample size of 15**

    $$
    \text{Subjective Value} = \frac{n_{lower}}{n_{higher} + n_{lower}}
    $$

    ```{r Function}
    ### FUNCTION TO CALCULATE DBS ###

    DBS <- function(magnitudes_list, sample_n) {
      
      # SET SEED FOR REPRODUCIBILITY 
      set.seed(2)
      
      
      # GENERATE SAMPLES
      data <- sample(magnitudes_list, size = sample_n, replace = FALSE)

      
      # CREATE AN EMPTY TIBBLE
      table <- tibble(element = numeric(0),
                      lower = list(), 
                      higher = list())

      
      for (i in seq_along(data)) {
        
        element <- data[i]          ## Select element
        elements_comp <- data[-i]   ## Select remaining elements minus the selected element
        
        
        # ESTABLISH EMPTY VARIABLES
        higher <- numeric(0)
        lower <- numeric(0)
        
        
        # COMPARE ELEMENTS
        for (j in seq_along(elements_comp)) {
          
          ## If remaining element is greater than selected element add it to higher vector
          if (element > elements_comp[j]) {
            higher <- c(higher, elements_comp[j])
          } 
          
          ## If remaining element is less than selected element add it to lower vector
          else {
            lower <- c(lower, elements_comp[j])
          }
        }
        
        
        # ADD VECTORS AS A LIST INTO THE TIBBLE TO MAKE IT EASIER TO IDENTIFY THE NUMBER OF ELEMENTS IN EACH VARIABLE (I.E., HIGHER OR LOWER)
        table <- add_row(table, element = element, 
                         lower = list(lower),
                         higher = list(higher))
      }
      
      
      # CREATE A NEW DBS TIBBLE FROM TABLE
      dbs_table <- table %>% 
        
        as_tibble() %>% 
        
        mutate(
          ## New column applying the DbS equation
          subjective_judgment = sapply(lower, length) / (sapply(lower, length) + sapply(higher, length)),
          
          ## New column identifying sample size 
          sample_size = sample_n,
          
          ## Establishing unique sample sizes as factors (useful for plotting)
          sample_size = factor(sample_size, levels = unique(sample_size))
          )
      
      dbs_table
      
    }
    ```

4.  **Vary sample size, skew of distribution**

    ```{r Sample_sizes}
    # VARYING SAMPLE SIZES
    n_5 <- DBS(c(1:20), 5)
    n_10 <- DBS(c(1:20), 10)
    n_15 <- DBS(c(1:20), 15)
    n_20 <- DBS(c(1:20), 20)

    # COMBINING ALL TIBBLES INTO ONE TIBBLE
    all_data <- bind_rows(n_5, n_10, n_15, n_20)

    print(all_data)

    # PLOTS
    ggplot(data = all_data, 
           aes(x = element, y = subjective_judgment, colour = sample_size)) +
      geom_point() +
      geom_line() + 
      
      scale_x_continuous(name = "Randomly sampled element", 
                         breaks = seq(0, 20, 4)) +
      scale_y_continuous(name = "Subjective Judgement",
                         breaks = seq(0, 1, 0.1)) +
      labs(colour = "Sample size") +
      
      theme_bw()
    ```

    ```{r Distributions}

    # VARYING DISTRIBUTION
    nskew_sample <- 20 * rbeta(20, 4, 1.2)
    pskew_sample <- 20 * rbeta(20, 1.2, 4)
    sskew_sample <- 20 * rbeta(20, 4, 4)

    nskew <- DBS(nskew_sample, 20)
    pskew <- DBS(pskew_sample, 20)
    sskew <- DBS(sskew_sample, 20)

    nskew <- nskew %>% 
      mutate(skew = "Negative")

    pskew <- pskew %>% 
      mutate(skew = "Positive")

    sskew <- sskew %>% 
      mutate(skew = "Symmetrical")

    all_data <- bind_rows(nskew, pskew, sskew)

    all_data <- all_data %>% 
      mutate(skew = factor(skew, levels = unique(skew)))

    print(all_data)

    # PLOT
    ggplot(data = all_data, 
           aes(x = element, y = subjective_judgment, colour = skew)) + 
      geom_point() +
      geom_line() +
      scale_x_continuous(name = "Randomly Sampled Element",
                         breaks = seq(0, 22, 2)) +
      scale_y_continuous(name = "Subjective Judgement",
                         breaks = seq(0, 1, 0.1)) +
      labs(colour = "Skew") +
      theme_bw()
    ```
