---
title: "Part 4 Agent Based Modelling (ABM)"
output: pdf_document

header-includes:
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 4 Explore and extend a simple Schelling segregation model

NOTE: DO NOT RUN FUNCTIONS IN RMD FILE RUN IN R FILE

## Circshift

```{r Circshift, eval=FALSE, echo=TRUE}
### CIRCULAR SHIFT FUNCTION ###

circshift <- function(x_to_be_shifted, shift_amount) {
  # Check for NULL input
  if (is.null(x_to_be_shifted)) return(x_to_be_shifted)
  
  #  Circular Shift for a Vector (1D)
  if (is.vector(x_to_be_shifted) && length(shift_amount) == 1) {
    n <- length(x_to_be_shifted)
    s <- shift_amount %% n
    x_to_be_shifted <- x_to_be_shifted[(1:n-s-1) %% n + 1]
  } 
  
  # Circular Shift for a Matrix (2D)
  else if (is.matrix(x_to_be_shifted) && length(shift_amount) == 2) {
    n <- nrow(x_to_be_shifted)
    m <- ncol(x_to_be_shifted)
    s1 <- shift_amount[1] %% n
    s2 <- shift_amount[2] %% m
    x_to_be_shifted <- x_to_be_shifted[(1:n-s1-1) %% n + 1, (1:m-s2-1) %% m + 1]
  } 
  
  # Error Handling
  else
    stop("Length of 'shift_amount' must be equal to the number of dimensions of 'x_to_be_shifted'.")
  
  # Returning the Shifted Vector or Matrix
  return(x_to_be_shifted)
}
```

\newpage

## Schelling Rules

1.  Academics are arranged in a spatial grid

2.  Each academic looks at their four (horizontal and vertical) neighbours

3.  An economist is unhappy if they have \>1 psychologists as neighbours

    A psychologist is unhappy if they have \>1 economists as neighbours

4.  On each time cycle, a random unhappy economist exchanges position with a random unhappy psychologist

5.  Happy academics don’t move

```{r Basic_Schelling_Function, eval=FALSE, echo=TRUE}
### BASIC SCHELLING FUNCTION ###


schelling_basic <- function(nside_inp) {
  ## STEP 1: SET UP WORLD WITH RANDOMLY POSITIONED ACADEMICS
  nside <- nside_inp  ## Number of agents on each side of the matrix

  ### Create an nside-by-nside matrix of random numbers between 0 and 1
  rand_world <- matrix(runif(nside^2, 0, 1),   # Generates nside^2 random numbers from a uniform distribution
                       nside,                  # Number of rows
                       nside                   # Number of columns
                       )

  ### Assign agents to be either Psychologists (0) or Economists (1)
  world <- (rand_world > .5) * 1
  #### If agent in rand_world is more than 0.5 it is assigned TRUE otherwise it is assigned FALSE. The boolean is then multiplied by 1 to return a numeric value 1 (TRUE = Economist) or 0 (FALSE = Psychologist)

  #### Alternative code: world = round(rand_world)
  ##### Works similarly as the above (i.e., if greater than 0.5, the agent is rounded to 1 and is labelled an Economist)

  ## Set up a colourmap where green represents Psychologists and red represents Economists
  agent_cols <- c(rgb(0, 1, 0), rgb(1, 0, 0))


  ## STEP 2: HAVE ACADEMICS CHECK THEIR NEIGHBOURS

  ### Give these temporary variables high values just to satisfy the while condition
  n_sad_econs <- nside^2
  n_sad_psychs <- nside^2

  while( min( c(n_sad_econs, n_sad_psychs) ) > 50 ) {
    ### Calculate number of Economists surrounding each agent
    A <- circshift(world, c(1, 0))         # Shift one row down and wrap round
    B <- circshift(world, c(-1, 0))        # Shift one row up and wrap round
    C <- circshift(world, c(0, 1))         # Shift one col right and wrap round
    D <- circshift(world, c(0, -1))        # Shift one col left and wrap round
    n_econ <- A + B + C + D                # Now matrix `n_econ` has the number of Economists neighbours for each person in world


  ## STEP 3: IDENTIFY SAD ECONOMISTS AND PSCYHOLOGISTS (still in the while loop)

    ### Find sad Economists (i.e. < 3 Economists as neighbours ~ > 1 Psychologists as neighbours)
    sad_econs <- world * (n_econ < 3) * 1

    ### Find sad Psychologists (i.e. > 1 Economists as neighbours)
    sad_psychs <- abs(world - 1) * (n_econ > 1) * 1

    ### Count the number of sad Psychologists and Economists
    n_sad_econs <- sum(sad_econs)
    n_sad_psychs <- sum(sad_psychs)


  ## STEP 4: SWAP SAD ACADEMICS (still in the while loop)

    ### Choose a random sad Economist and change to be a Psychologist
    w <- which(sad_econs > 0, arr.ind = TRUE)              # Get the row and col indices (arr.ind = TRUE) of all sad Economists (sad_econs > 0)
    index <- ceiling(runif(1, 0, 1) * n_sad_econs)         # Choose a random sad Economist
    world[w[index, 1], w[index, 2]] <- 0                   # Change the Economist to a Psychologist

    ### Choose a random sad Psychologist and change to be an Economist
    w <- which(sad_psychs > 0, arr.ind = TRUE)            # Get the row and col indices of all sad Psychologists
    index <- ceiling(runif(1, 0, 1) * n_sad_psychs)       # Choose a random sad Economist
    world[w[index, 1], w[index, 2]] <- 1                  # Change the Economist to a Psychologist

  ## STEP 5: DRAW THE STATE OF THE WORLD
    
    image(world, col = agent_cols)
    Sys.sleep(0.2)      # Update the figure each time it goes round

  }
}
```

\newpage

## Task 4.1: Understand and extend the code.

```{r Schelling_Final_Function, eval=FALSE, echo=TRUE}
### EDITED SCHELLING FUNCTION ###


schelling_final_model <- function(nside_inp, psych_n, econ_econ, psych_econ) {
  
  # STEP 1: SET UP WORLD WITH RANDOMLY POSITIONED ACADEMICS
  ## CHANGES MADE FOR LARGER NEIGHBOURHOODS
  nside <- nside_inp     ## Number of agents on each side of the matrix

  ### Create an nside-by-nside matrix of random numbers between 0 and 1
  rand_world <- matrix(runif(nside^2, 0, 1),   # Generates nside^2 random numbers from a uniform distribution
                       nside,                  # Number of rows
                       nside                   # Number of columns
                       )

  ### CHANGES MADE SO THERE ARE MORE PSYCHOLOGISTS THAN ECONOMISTS
  ### Assign agents to be either Psychologists (0) or Economists (1)
  world <- (rand_world > psych_n) * 1
  #### If agent in rand_world is more than `psych_n` it is assigned TRUE otherwise it is assigned FALSE. The boolean is then multiplied by 1 to return a numeric value 1 (TRUE = Economist) or 0 (FALSE = Psychologist)

  ## Set up a colourmap where green represents Psychologists and red represents Economists
  agent_cols <- c(rgb(0, 1, 0), rgb(1, 0, 0))


  # STEP 2: HAVE ACADEMICS CHECK THEIR NEIGHBOURS

  ### Give these temporary variables high values just to satisfy the while condition
  n_sad_econs <- nside^2
  n_sad_psychs <- nside^2

  while( min( c(n_sad_econs, n_sad_psychs) ) > nside ) {
    ### Calculate number of Economists surrounding each agent
    A <- circshift(world, c(1, 0))     # Shift one row down and wrap round
    B <- circshift(world, c(-1, 0))    # Shift one row up and wrap round
    C <- circshift(world, c(0, 1))     # Shift one col right and wrap round
    D <- circshift(world, c(0, -1))    # Shift one col left and wrap round
    n_econ <- A + B + C + D            # Now matrix `n_econ` has the number of Economists neighbours for each person in world


  # STEP 3: IDENTIFY SAD ECONOMISTS AND PSCYHOLOGISTS (still in the while loop)

    ## CHANGES MADE SO ECONOMISTS/PSYCHOLOGISTS CAN TOLERATE TWO DIFFERENT NEIGHBOURS
    ### Find sad Economists (i.e. < `econ_econ` Economists as neighbours ~ > (4 - `econ_econ`) Psychologists as neighbours)
    sad_econs <- world * (n_econ < econ_econ) * 1

    ### Find sad Psychologists (i.e. > `psych_econ` Economists as neighbours)
    sad_psychs <- abs(world - 1) * (n_econ > psych_econ) * 1

    ### Count the number of sad Psychologists and Economists
    n_sad_econs <- sum(sad_econs)
    n_sad_psychs <- sum(sad_psychs)


  # STEP 4: SWAP SAD ACADEMICS (still in the while loop)

    ### Choose a random sad Economist and change to be a Psychologist
    w <- which(sad_econs > 0, arr.ind = TRUE)         # Get the row and col indices (arr.ind = TRUE) of all sad Economists (sad_econs > 0)
    index <- ceiling(runif(1, 0, 1) * n_sad_econs)    # Choose a random sad Economist
    world[w[index, 1], w[index, 2]] <- 0              # Change the Economist to a Psychologist

    ### Choose a random sad Psychologist and change to be an Economist
    w <- which(sad_psychs > 0, arr.ind = TRUE)        # Get the row and col indices of all sad Psychologists
    index <- ceiling(runif(1, 0, 1) * n_sad_psychs)   # Choose a random sad Economist
    world[w[index, 1], w[index, 2]] <- 1              # Change the Economist to a Psychologist

  # STEP 5: DRAW THE STATE OF THE WORLD
    
    image(world, col = agent_cols)
    Sys.sleep(0.2)      # Update the figure each time it goes round

  }
}
```

```{r Functions, eval=FALSE, echo=TRUE}
### APPLYING BOTH FUNCTIONS ###

schelling_basic(50)

schelling_final_model(50, 0.5, 3, 1)
```

\newpage

1.  **What happens (and why) if:**

    1.  **Economists, psychologists, or both can tolerate two different neighbours?**

        ```{r Code_Tolerance, eval=FALSE, echo=TRUE}
        ### CODE CHANGES MADE SO ECONOMISTS/PSYCHOLOGISTS CAN TOLERATE TWO DIFFERENT NEIGHBOURS ###

        # Find sad Economists (i.e. < `econ_econ` Economists as neighbours ~ > (4 - `econ_econ`) Psychologists as neighbours)
        sad_econs <- world * (n_econ < econ_econ) * 1

        # Find sad Psychologists (i.e. > `psych_econ` Economists as neighbours)
        sad_psychs <- abs(world - 1) * (n_econ > psych_econ) * 1

        # Count the number of sad Psychologists and Economists
        n_sad_econs <- sum(sad_econs)
        n_sad_psychs <- sum(sad_psychs)
        ```

        ```{r Better_Tolerance, eval=FALSE, echo=TRUE}
        ### ECONOMISTS CAN TOLERATE TWO DIFFERENT NEIGHBOURS ### 
        # Sad Economists: < 2 Economists as neighbours so > 2 Psychologists as neighbours
        # Sad Psychologists: > 1 Economists as neighbours (criteria remains unchanged)
        schelling_final_model(50, 0.5, 2, 1)


        ### PSYCHOLOGISTS CAN TOLERATE TWO DIFFERENT NEIGHBOURS ### 
        # Sad Economists: < 3 Economists as neighbours so > 1 Psychologists as neighbours (criteria remains unchanged)
        # Sad Psychologists: > 2 Economists as neighbours
        schelling_final_model(50, 0.5, 3, 2)


        ### ECONOMISTS AND PSYCHOLOGISTS CAN TOLERATE TWO DIFFERENT NEIGHBOURS ### 
        # Sad Economists: < 2 Economists as neighbours so > 2 Psychologists as neighbours
        # Sad Psychologists: > 2 Economists as neighbours
        schelling_final_model(50, 0.5, 2, 2)
        ```

        \newpage

    2.  **There are initially more psychologists than economists**

        ```{r Code_More_Psych, eval=FALSE, echo=TRUE}
        ### CODE CHANGES MADE SO THERE ARE MORE PSYCHOLOGISTS THAN ECONOMISTS ###

        ## Assign agents to be either Psychologists (0) or Economists (1)
        world <- (rand_world > psych_n) * 1
        ## If agent in rand_world is more than `psych_n` it is assigned TRUE otherwise it is assigned FALSE. The boolean is then multiplied by 1 to return a numeric value 1 (TRUE = Economist) or 0 (FALSE = Psychologist)
        ```

        ```{r More_Psych, eval=FALSE, echo=TRUE}
        ### MORE PSYCHOLOGISTS ###
        schelling_final_model(50, 0.75, 3, 1)
        ```

    3.  **Look at larger neighbourhoods (harder)**

        ```{r Code_Larger_Neighbourhood, eval=FALSE, echo=TRUE}
        ### CODE CHANGES MADE FOR LARGER NEIGHBOURHOODS ###

        nside <- nside_inp     ## Number of agents on each side of the matrix
        ```

        ```{r Larger_Neighbourhood, eval=FALSE, echo=TRUE}
        ### LARGER NEIGHBOURHOODS ###

        schelling_final_model(75, 0.5, 3, 1)
        ```
